\documentclass[a4paper,11pt]{article}

% --------------------------------------------------
% Engine requirement
% --------------------------------------------------
\usepackage{iftex}
\ifPDFTeX
  \errmessage{This manual must be compiled with XeLaTeX or LuaLaTeX}
\fi

% --------------------------------------------------
% Packages
% --------------------------------------------------
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{titlesec}

% --------------------------------------------------
% Page layout
% --------------------------------------------------
\geometry{margin=25mm}

% --------------------------------------------------
% Fonts
% --------------------------------------------------
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}

% --------------------------------------------------
% Hyperref setup
% --------------------------------------------------
\hypersetup{
  colorlinks=true,
  linkcolor=black,
  urlcolor=blue,
  pdftitle={modernnewspaper Package Manual},
  pdfauthor={Laitei}
}

% --------------------------------------------------
% Listings setup
% --------------------------------------------------
\lstset{
  basicstyle=\ttfamily\small,
  frame=single,
  breaklines=true,
  keywordstyle=\color{blue}
}

% --------------------------------------------------
% Title info
% --------------------------------------------------
	itle{\textbf{modernnewspaper}\\
A Modern Newspaper Package for LaTeX}
\author{Laitei}
\date{Version 0.1.0 --- January 2026}

\begin{document}

\maketitle

\section{Introduction}

The \textbf{modernnewspaper} package is a modern, Unicode-first LaTeX
package for creating newspaper-style documents. It is designed as a
clean and extensible alternative to the legacy \texttt{newspaper}
package.

The package supports modern typographic workflows, multilingual text,
and web-oriented metadata such as website URLs, while remaining suitable
for print output.

\section{Requirements}

This package \textbf{requires} one of the following engines:

\begin{itemize}
  \item XeLaTeX
  \item LuaLaTeX
\end{itemize}

The package does \textbf{not} support pdfLaTeX, as Unicode support is
mandatory.

\section{Installation}

\subsection{Local Installation}

Copy \texttt{modernnewspaper.sty} into the same directory as your
\texttt{.tex} file.

\subsection{User Installation}

Alternatively, install it into your local \texttt{texmf} tree:

\begin{verbatim}
~/texmf/tex/latex/modernnewspaper/
\end{verbatim}

\section{Basic Usage}

Load the package in the document preamble:

\begin{lstlisting}
\usepackage{modernnewspaper}
\end{lstlisting}

\section{Metadata Commands}

The following commands configure the newspaper metadata:

\begin{lstlisting}
\SetPaperName{Modern Newspaper}
\SetPaperSlogan{Informing the future}
\SetPaperLocation{Yangon, Myanmar}
\SetPaperWebsite{https://example.com}
\SetPaperVolume{1}
\SetPaperIssue{1}
\SetPaperDate{\today}
\end{lstlisting}

\section{Masthead}

To typeset the newspaper masthead, use:

\begin{lstlisting}
\MakePaperHeader
\end{lstlisting}

This command prints the paper name, slogan, location, volume, issue,
date, and website URL.

\section{Columns}

Newspaper content is typically set in multiple columns.

\begin{lstlisting}
\BeginNewsColumns{2}
% content
\EndNewsColumns
\end{lstlisting}

The number of columns may be adjusted as needed.

\section{Articles}

Articles are created using the \texttt{article} environment together
with headline and byline commands.

\subsection{Headline}

\begin{lstlisting}
\headline{Article Title}
\end{lstlisting}

\subsection{Byline}

\begin{lstlisting}
\byline{Author Name}
\end{lstlisting}

\subsection{Article Environment}

\begin{lstlisting}
\begin{article}
\headline{Sample Article}
\byline{Editor}

This is the article body text.
\end{article}
\end{lstlisting}

\section{Unicode Support}

The \textbf{modernnewspaper} package fully supports Unicode text. For
example:

\begin{quote}
မြန်မာစာ · العربية · हिन्दी · 中文 · English
\end{quote}

No additional configuration is required.

\section{Customization}

Users may redefine headline and byline styles:

\begin{lstlisting}
\renewcommand{\headlinestyle}{\Large\bfseries}
\renewcommand{\bylinestyle}{\itshape}
\end{lstlisting}

\section{Limitations}

Current version limitations include:

\begin{itemize}
  \item No built-in image wrapping
  \item No drop caps
  \item No theme system
  \item Limited RTL support
\end{itemize}

These features are planned for future releases.

\section{Roadmap}

Planned improvements include:

\begin{itemize}
  \item Drop caps
  \item Image-wrapped articles
  \item RTL language support
  \item Theme system
  \item Accessibility improvements
  \item CTAN submission
\end{itemize}

\section{License}

This package is distributed under the
\textbf{LaTeX Project Public License (LPPL) v1.3c}.

See the \texttt{LICENSE} file or visit:
\begin{center}
\url{https://www.latex-project.org/lppl.txt}
\end{center}

\section{Contact}

Project repository:

\begin{center}
\url{https://github.com/laitei/modernnewspaper}
\end{center}

\end{document}
